\textsc{spiderman}: an open source code to model phase curves and secondary eclipses.

### 2016-10-18 ms.tex
examples
finalised figures

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/zhang_quad.pdf}
\caption{An example of the temperature distribution generated by using the Zhang model. Clockwise from top left: Phase = 0.0,0.25,0.75,1.0}
\label{fig:zhang_quad}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/zhang_quad_bright.pdf}
\caption{Same as \ref{fig:zhang_quad}, but the scale is now flux instead of temperature. A blackbody spectrum and a channel of 1.1-1.7 microns was assumed to make the conversion. The option exists to add limb darkening to this profile.}
\label{fig:zhang_quad2}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/sphere_quad.pdf}
\includegraphics[width=\columnwidth]{img/spherical_lc.pdf}
\caption{A model generated using spherical harmonics}
\label{fig:harmonics}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/zhang_lc.pdf}
\caption{An example lightcurve generated using the distribution in figure \ref{fig:zhang_quad}}
\label{fig:zhang_lc}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/zhang_lc_zoom.pdf}
\caption{A close up of the secondary eclipse in figure \ref{fig:zhang_lc}. Note the different shape of the ingress and egress, caused by the asymmetry in the flux distribution on the planet.}
\label{fig:zhang_zoom}
\end{center}
\end{figure}

\subsection{Model design}\label{sec:fitting}

@@

@@

Will display the planet from the perspective of the observer on Earth at the desired phase or Julian date.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/system.pdf}
\caption{An example of the graphical output that \textsc{spiderman} can produce. This image is a scale representation of the system, with the planetary flux map included. This is useful for visualising the model. It was generated with the spiderman.plot\_system() command. The image of the star is purely aesthetic, and does not contain any model detail.}
\label{fig:plot_system}
\end{center}
\end{figure}

@@

Fortunately, the phasing of the observations is such that the three visits cover very different ranges of the phase curve, which does tend to alleviate the degeneracy. As can be seen in the large corner plot in figure \ref{}, these parameters are still degenerate with the physical model parameters, in particular the $\xi$ paramter which controls the phase curve shape, but the constraints placed on these parameters are still useful, and marginalising over the systematics parameters with the MCMC should remove any doubt that the results are only an artefact.

@@

T.L. is supported by a STFC studentship. P.W. is supported by a STFC consolidated grant (ST/L000733/1).

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/sphere_quad.pdf}
\caption{A model generated using spherical harmonics}
\label{fig:harmonics}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{img/both_lc.pdf}
\includegraphics[width=\columnwidth]{img/both_lc_zoom.pdf}
\caption{A close up of the secondary eclipse in figure \ref{fig:ex_lcs}. Note the different shape of the ingress and egress, caused by the asymmetry in the flux distribution on the planet.}
\label{fig:ex_lcs}
\end{center}
\end{figure}

\subsection{integrator design}\label{sec:integrator}

@@

\subsection{Flux conversions}\label{sec:flux conversions}

\subsection{Stellar models}\label{sec:stellar models}

@@

Will display the planet from the perspective of the observer on Earth at the desired phase or Julian date. If the chosen model uses a temperature distribution, then these plots can be made for both the temperature and the calculated flux distribution.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{img/system.pdf}
\caption{An example of the graphical output that \textsc{spiderman} can produce. This image is a scale representation of the system, with the planetary flux map included. This is useful for visualising the model. It was generated with the spiderman.plot\_system() command. The image of the star is purely aesthetic, and does not contain any model detail.}
\label{fig:plot_system}
\end{center}
\end{figure*}

@@

Fortunately, the phasing of the observations is such that the three visits cover very different ranges of the phase curve, which does tend to alleviate the degeneracy. As can be seen in the large corner plot in figure \ref{fig:big triangle}, these parameters are still degenerate with the physical model parameters, in particular the $\xi$ paramter which controls the phase curve shape, but the constraints placed on these parameters are still useful, and marginalising over the systematics parameters with the MCMC should remove any doubt that the results are only an artefact.

@@
